On the performance of the MAC model

### 2018-10-31 2018_nips_vigil/mac.tex
Fixing MAC section

The MAC network~\cite{hudson2018compositional} is a recurrent model that performs reasoning 
using multiple steps, where each step involves sequentially analyzing a part of the question following which attention on the image is changed suitably.
At the end, a suitable answer is given based on this composite reasoning.
To improve the accuracy of prediction, both the questions and images
are preprocessed suitably. For the question,  a word-embedding is first used to
transformed the question into a sequence of vectors which is then passed through
a bidirectional LSTM to produce a sequence of hidden state pairs. Each such pair 
corresponds to a unique word in the question and is called the 
\emph{contextual embedding} for that word.
Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.

>>>>

The MAC network~\cite{hudson2018compositional} is a recurrent model that performs
sequential reasoning, where each step involves analyzing a part of the question following 
which attention on the image is changed suitably.
At the end, a suitable answer is given based on this composite reasoning.
Both the question and image are transformed suitably prior to the reasoning process. 
For the question, a sequence of vectors obtained via word-embeddings is fed
to a bidirectional LSTM to produce a sequence of hidden state pairs. Each pair 
corresponds to a unique word in the question and denotes its 
\emph{contextual embedding}. The final states in each direction 
represent the \emph{global context} of that question.
Similarly each image is initially processed using a pre-trained network (using ResNet~\cite{he2016resnet}) to obtain a feature map. 
This is used as an input to a trainable neural network that consists of 
two CNN layers followed by a single linear layer\footnote{%
This minor reformulation saves computation time instead of applying it
in \emph{every} reasoning step.}.
This results in a 3D tensor for each image in the data set collectively called the
\emph{knowledge base}~\cite{hudson2018compositional}.
